---
title: "p8015_hw1_ax2173"
output: github_document
---

```{r setup}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

## Problem 1

Import the data.

```{r import data}
data("penguins", package = "palmerpenguins")
```

Omit the NA to calculate the mean of flipper_length_mm

```{r omit the NA to calculate the mean of flipper_length_mm}
penguins2 = na.omit(penguins)
```

* These are some descriptions of this dataframe:
  * This dataframe includes these varibales: `r colnames(penguins)`
  * This dataset has `r nrow(penguins)` rows, and  `r ncol(penguins)` columns.
  * The mean flipper length is `r round(mean(penguins2$flipper_length_mm),2)`.
  
```{r make a scatterplot and save it to my project directory}
ggplot(penguins2, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot_peguins.pdf")
```



## Problem 2

First, create the dataframe.

```{r create a dataframe}
p2_df = tibble(
  nrom = rnorm(10),
  logical = nrom > 0,
  char = c('1','2','3','4','5','6','7','8','9','10'),
  fac = factor(c('2','1','1','2','2','3','1','3','3','2'))
)
```

Then, convert the logical, character, factor variables to numeric character.

```{r convert variables}
logical_num = as.numeric(pull(p2_df, var = logical))
char_num = as.numeric(pull(p2_df, var = char))
fac_num = as.numeric(pull(p2_df, var = fac))
```

Calculate the mean of variables in the dataframe.

```{r calculate the mean of each variable}
mean(pull(p2_df, var = nrom))
mean(logical_num)
mean(char_num)
mean(fac_num)
```
